msc dissertation

### 2021-07-20 msc dissertation code.Rmd
latest

#successful screen3 test (result = 3)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3_2,1)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,2)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,4)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,5)
#to check if screen 3 successful
mean(pennystudy2r1$screen3, na.rm = TRUE)

#replace 2 and 3 to 1
pennystudy2r1["screen1"][pennystudy2r1["screen1"] == 2] <- 1
pennystudy2r1["screen2"][pennystudy2r1["screen2"] == 2] <- 1
pennystudy2r1["screen3"][pennystudy2r1["screen3"] == 3] <- 1

>>>>

#successful screen3 test (result = 3)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3_2,1)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,2)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,4)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,5)
#check if screen 3 successful
mean(pennystudy2r1$screen3, na.rm = TRUE)

#re-code screen test: replace 2 and 3 to 1
pennystudy2r1["screen1"][pennystudy2r1["screen1"] == 2] <- 1
pennystudy2r1["screen2"][pennystudy2r1["screen2"] == 2] <- 1
pennystudy2r1["screen3"][pennystudy2r1["screen3"] == 3] <- 1
